---
title: "Details Agile Project Data Set"
output:
  github_document:
    html_preview: false
---

---

This R-Notebook is a short introduction to the __agile project dataset__. The data set contains anonymized project data from Jira.

```{r}
require(ggplot2)
```

The whole data set is stored in a csv file. Some of the observation may not make sense. For example there are observations with a cycle time _-1_. During a "migration or cleanup session" this may resulted in some cases where finished date is before the created date.

```{r}
df <- read.csv('data/jira.csv', sep = ',', header = T)
df$created_date <- as.Date(df$created_date)
df$finished_date <- as.Date(df$finished_date)
df$project <- as.factor(df$project)

head(df)
summary(df)
```

The data set contains data from different years. 

```{r}
freq_year <- data.frame(table(format(df$created_date, format='%Y')))
names(freq_year) <- c('year', 'freq')
ggplot(data=freq_year, aes(x=year, y=freq)) + geom_bar(stat="identity")

```

## Project Data from 2018

Let's inspect the data from 2018.

```{r}
df <- df[df$created_date > '2017-12-31',]
df <- df[df$cycle_time_days > -1,]
head(df)
```



We can plot the histogram of the cycle times from 2018.

```{r}
ggplot(df, aes(x=cycle_time_days)) + geom_histogram(bins = 20)
```

Another interesting aspect is the boxplot for the two projects in 2018.

```{r}
ggplot(df, aes(x = project, y = cycle_time_days)) + geom_boxplot()
```

### T-Test

Now we can use a t-test to compare the two project cycle times.

```{r}
t.test(df$cycle_time_days ~ df$project, var.equal = FALSE) 
```

```{r}
t.test(df$cycle_time_days ~ df$project, var.equal = TRUE) 
```

### Time Series

Let's plot the time series data when Jira task were finished.

```{r}
freq <- table(finished_date = df$finished_date)



time_series <- data.frame(freq)
time_series$finished_date <- as.Date(time_series$finished_date)
names(time_series) <- c('finished_date', 'freq')


ggplot( data = time_series, aes( finished_date, freq )) + geom_line() 
```

